Detecting Hand Direction for Computer Interaction

### 2014-12-10 paper/paper.tex
Paper edits.

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{gensymb}

@@

\subsection{Data collection and evaluation}

@@

For evaluation, we used 15-fold cross validation, except the groups were chosen based on the grid collection iteration instead of a random sample.  For each data group, we trained on the other 14 groups and evaluated performance on the group, then we took the average performance for all 15 groups.  The reason for choosing groups based on collection iteration instead of random sampling is that images collected during the same scanning process tended to be more similar so training with images in the same iteration as the test data artificially increased scores.

@@

\begin{figure}[t]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointImage.png}
			\caption{} % Just to get the (a)
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointLeft2Image.png}
			\caption{}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointHOGedit.png}
			\caption{}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointLeft2HOGedit.png}
			\caption{}
		\end{subfigure}
	\end{center}
	\caption{An image (on the left) and our corresponding HOG output (on the right). The location calculated by our algorithm is illustrated by the blue dot on the left image.}
	\label{fig:pointImages}
\end{figure}

@@

@@

\subsubsection{Performance of Different Regressions}
We evaluated the performance of both convolution neural networks and HOG with k-Nearest Neighbors and Linear Regression. The results from our tests our given in figure \ref{fig:hist}, which is a histogram of the error of the different classifiers. The error is the euclidean distance measured in pixels between the predicted point and the actual point.
\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[width=0.9\linewidth]{figures/ClassifierErrorHist.png}
	\end{center}
	\caption{}
	\label{fig:hist}
\end{figure*}

\begin{figure*}
	% Figure on bad images
	\begin{center}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointLeftImage.png}
			\caption{} % Just to get the (a)
			\label{fig:pointLeftImage}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointRightImage.png}
			\caption{}
			\label{fig:pointRightImage}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointLeftHOG.png}
			\caption{}
			\label{fig:pointLeftHog}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointRightHOG.png}
			\caption{}
			\label{fig:pointRightHog}
		\end{subfigure}
	\end{center}
	\caption{Examples of images in which our algorithm does not perform as well. The hand is pointing to different points on the screen in images \ref{fig:pointLeftImage} and \ref{fig:pointRightImage}. However, the HOG outputs in \ref{fig:pointLeftHog} and \ref{fig:pointRightHog} are almost identical. This happens because the HOG algorithm mostly detects the outline of the hand and not the pointing finger which is facing mostly toward the camera. Because the HOG images are so similar, the regression does not train properly, causing the blue cursor in \ref{fig:pointLeftImage} and \ref{fig:pointRightImage} to be in the incorrect location.}
	\label{fig:close}
\end{figure*}

\begin{tabular}{|c|c|}
	\hline
	\multicolumn{2}{|c|}{\textbf{Errors for Convolution Neural Nets}}\\\hline
	\textbf{Regression Type} & \textbf{Average Error (Pixels)} \\\hline
	k-Nearest Neighbors & 47.8 \\\hline
	Linear Regression &  114.2 \\\hline	
\end{tabular}

\begin{tabular}{|c|c|}
	\hline
	\multicolumn{2}{|c|}{\textbf{Errors for Histogram of Oriented Gradients}} \\\hline
	\textbf{Regression Type} & \textbf{Average Error (Pixels)} \\\hline
	k-Nearest Neighbors & 32.0\\\hline
	Linear Regression & 79.7 \\\hline
	Combined & 47.0 \\\hline
\end{tabular}

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{gensymb}

@@

\subsection{Data collection}

@@

@@

@@

\subsection{Evaluation}
For evaluation, we used 15-fold cross validation, except the groups were chosen based on the grid collection iteration instead of a random sample.  For each data group, we trained on the other 14 groups and evaluated performance on the group, then we took the average performance for all 15 groups.  The reason for choosing groups based on collection iteration instead of random sampling is that images collected during the same scanning process tended to be more similar so training with images in the same iteration as the test data artificially increased scores.

@@

\subsubsection{Performance of Different Regressions}
We evaluated the performance of both convolutional neural networks and HOG with k-Nearest Neighbors and Linear Regression. We used this data to aid us in selecting a regression method. The results from our tests our given both in the table below and in figure \ref{fig:hist}, which is a histogram of the error of the different classifiers. The error is the euclidean distance measured in pixels between the predicted point and the actual point.

\begin{table}
	\caption{}
	\begin{center}
		\begin{tabular}{|c|c|}
			\hline
			\multicolumn{2}{|c|}{\textbf{Errors for Convolution Neural Nets}}\\\hline
			\textbf{Regression Type} & \textbf{Average Error (Pixels)} \\\hline
			k-Nearest Neighbors & 47.8 \\\hline
			Linear Regression &  114.2 \\\hline	
		\end{tabular}
		\begin{tabular}{|c|c|}
			\hline
			\multicolumn{2}{|c|}{\textbf{Errors for Histogram of Oriented Gradients}} \\\hline
			\textbf{Regression Type} & \textbf{Average Error (Pixels)} \\\hline
			k-Nearest Neighbors & 32.0\\\hline
			Linear Regression & 79.7 \\\hline
			Combined & 47.0 \\\hline
		\end{tabular}
	\end{center}
	\label{table:meanErrors}
\end{table}

The k-Nearest Neighbors algorithm when applied to HOG yields the highest accuracy as can be seen from both the mean error in Table \ref{table:meanErrors} and the error distribution in Figure \ref{fig:hist}.

\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[width=0.9\linewidth]{figures/ClassifierErrorHist.png}
	\end{center}
	\caption{}
	\label{fig:hist}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointImage.png}
			\caption{} % Just to get the (a)
			\label{fig:pointImage}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointLeft2Image.png}
			\caption{}
			\label{fig:pointLeft2Image}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointHOGedit.png}
			\caption{}
			\label{fig:pointHogEdit}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointLeft2HOGedit.png}
			\caption{}
			\label{fig:pointLeft2HogEdit}
		\end{subfigure}
	\end{center}
	\caption{The above images \ref{fig:pointImage} and \ref{fig:pointLeft2Image} demonstrate the correct output of our algorithm. The corresponding HOG features of each image can be seen below in \ref{fig:pointHogEdit} and \ref{fig:pointLeft2HogEdit}. The algorithm works well when the entire pointer finger is visible against the background as illustrated by \ref{fig:pointImage} or when some portion of the pointer finger is visible against the background, even if much of it is located in front of the rest of the hand as shown in \ref{fig:pointLeft2Image}.}
	\label{fig:pointImages}
\end{figure}
\begin{center}
\begin{figure*}[t]
	% Figure on bad images
	\begin{center}
		\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{figures/PointLeftImage.png}
			\caption{} % Just to get the (a)
			\label{fig:pointLeftImage}
		\end{subfigure}
		\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{figures/PointRightImage.png}
			\caption{}
			\label{fig:pointRightImage}
		\end{subfigure}
		~\\
		\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{figures/PointLeftHOG.png}
			\caption{}
			\label{fig:pointLeftHog}
		\end{subfigure}
		\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{figures/PointRightHOG.png}
			\caption{}
			\label{fig:pointRightHog}
		\end{subfigure}
	\end{center}
	\caption{Examples of images in which our algorithm does not perform as well. The hand is pointing to different points on the screen in images \ref{fig:pointLeftImage} and \ref{fig:pointRightImage}. However, the HOG outputs in \ref{fig:pointLeftHog} and \ref{fig:pointRightHog} are almost identical. This happens because the HOG algorithm mostly detects the outline of the hand and not the pointing finger which is facing mostly toward the camera. Because the HOG images are so similar, the regression does not train properly, causing the blue cursor in \ref{fig:pointLeftImage} and \ref{fig:pointRightImage} to be in the incorrect location.}
	\label{fig:pointErrors}
\end{figure*}
\begin{figure*}[b]
	% Figure on bad images
	\begin{center}
		\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{figures/PointFarImage.png}
			\caption{} % Just to get the (a)
			\label{fig:pointFarImage}
		\end{subfigure}
		\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{figures/PointCloseImage.png}
			\caption{}
			\label{fig:pointCloseImage}
		\end{subfigure}
		~\\
		\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{figures/PointFarHOG.png}
			\caption{}
			\label{fig:pointFarHog}
		\end{subfigure}
		\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{figures/PointCloseHOG.png}
			\caption{}
			\label{fig:pointCloseHog}
		\end{subfigure}
	\end{center}
	\caption{The above images \ref{fig:pointFarImage} and \ref{fig:pointCloseImage} illustrate the difficulty in tracking the exact position of the pointer finger when it is pointing perpendicular to the camera. The finger in \ref{fig:pointCloseImage} is pointing more toward the camera than the finger in \ref{fig:pointFarImage}, but it is difficult for even a human to distinguish between the two. The HOG images \ref{fig:pointFarHog} and \ref{fig:pointCloseHog} are nearly indistinguishable as a result.}
	\label{fig:close}
\end{figure*}
\end{center}
\FloatBarrier
